---
title: "Week 4 - Developing Data Products"
author: "Chris Norris"
date: "25 August 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is Week 4 of the Developing Data Products course from the Coursera Data Science Specialisation.

My submission comprises two parts:

- The Shiny Application found at https://nozzo.shinyapps.io/Popular_Equations/
- The Reproducable Pitch Presentation which you are reading now.
- All files are shown in Github at https://github.com/nozzo1/week4

## How it works

The interface asks you to select a formula in the side bar that you are interested in calculating a value for.
You then enter two values which can be a side length or radius as Parameter 1 and another side length or height as Parameter 2.  
  
For example; A rectangle area calulation requires two side lengths whereas a cone volume requires a radius and height. There are default values of '10' for both intially.  
  
The application will automatically apply the two parameters to the formula chosen via the radio buttons.

## Slide with R Output

Converting formula to R is relatively easy.   
Let's take the formula for the volume of a cone as an example:
\[
\begin{eqnarray}
\frac{\mathbb{\pi}\times radius^2 \times height}{3}\\
\end{eqnarray}
\]

So to take the example of a cone with radius of 10 and a height of 20 we write in R:

```{r, echo = TRUE}
answer <- ((3.1416 * (10)^2) * 20)/3
print(answer)
```

## Formula selection mechanism

For this simple example I chose to use the R switch command in conjunction with renderprint and the output from the input as inFormula. Now R has a list of formulas to apply the two parameters to which is piped back in to the output as 'oAnswer'.


```
output$oAnswer    <- renderPrint({switch(input$inFormula,
 "Area - Rectangle" = (input$inParam1 * input$inParam2), 
 "Area - Triangle" = ((input$inParam1 * input$inParam2)/2), 
 "Volume - Pyramid" = ((input$inParam1 * input$inParam2)/3), 
 "Volume - Cylinder" = ((3.1416 * (input$inParam1)^2) * input$inParam2), 
 "Volume - Cone" = ((3.1416 * (input$inParam1)^2) * input$inParam2)/3 
 )})
```

Although this works well it would not scale up beyond 20 or so. Therefore if I expand this in to the future I will store these in a data frame for switch selection.

## Final

Thank you for reading my presentation.   
I hope you enjoy using my formula Shiny based application.   
I look forward to your feedback.   
   
Thanks   
Chris Norris   
August 2017
